---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# SEEEapi

<!-- badges: start -->
<!-- badges: end -->

The goal of SEEEapi is to provide an easy way to access the indicator calculation services from the [French system for evaluating water status](http://seee.eaufrance.fr/)

## Installation

You can install the released version of SEEEapi from [GitHub](https://github.com) with:

``` r
#install.packages(remotes)
remotes::install_github("CedricMondy/SEEEapi)
```

## Example

### List of available indicators

You can list all available indicators :

```{r example}
library(SEEEapi)
get_indic()
```
You can also list only the indicators from a given type:

```{r}
get_indic(type = "diagnostic")
```


### Run calculations

The calculations can be executed online on the SEEE server:

```{r, eval=FALSE}
calc_indic(indic      = "IPR", 
           version    = "1.0.3", 
           file_paths = c("IPR_entree_01_env.txt", "IPR_entree_02_faun.txt"))
```

```{r, echo=FALSE}
calc_indic(indic = "IPR", 
           version = "1.0.3", 
           file_paths = c("dev/IPR_entree_01_env.txt", "dev/IPR_entree_02_faun.txt"))
```

The calculation can also be executed locally by providing a directory where the scripts will be saved (either using `get_algo` or directly by `calc_indic`):

```{r, eval=FALSE}
calc_indic(indic    = "IPR",
           version  = NULL,                     # default value, will use the most
                                                # recent version available
           data     = list(IPR_entree_01_env,   # can use data from the environment
                           IPR_entree_02_faun), # instead of file paths
           locally  = TRUE,
           dir_algo = "my/path/to/algos")
```

